Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-09-08 Code_journal1/paperTNSM/pr.tex
last version of paper 1

 %\pdfoutput=1
%\documentclass[conference]{IEEEtran}
\documentclass[lettersize,journal]{IEEEtran}
\normalsize
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{setspace}
\usepackage{array,tabulary,tabularx,multirow}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{caption}
\captionsetup{font=footnotesize}
\usepackage{algcompatible}
%\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{stackengine}
%\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage[dvipsnames]{xcolor}
\usepackage{algorithm}
\usepackage{algorithmicx}
%\usepackage{algorithmic,algorithm2e,float}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{balance}
\usepackage{booktabs}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\setlength{\columnsep}{11mm}
\captionsetup{font=footnotesize}
\captionsetup[figure]{font=small}
\newcommand{\abstractnamefont}{\normalfont\small\bfseries}
\newcommand{\abstracttextfont}{\normalfont\small}
\setlength{\belowcaptionskip}{-10pt}
\def\hlinewd#1{%
\noalign{\ifnum0=`}\fi\hrule \@height #1 %
\futurelet\reserved@a\@xhline} 
%\setlength{\dbltextfloatsep}{-20pt}
\begin{document}

\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%}
\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, Saeede Parsaeefard$^\dagger$, and Onel Luis Alcaraz López$^\ddagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com, \{onel.alcarazlopez\}@oulu.fi\\
\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada, $^\ddagger$University of Oulu, Oulu, Finland}
 }
\maketitle
\pagenumbering{gobble}
%\vspace*{-4em}
\begin{abstract}
%\vspace*{-1.5em}
The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks. Nevertheless, strictly satisfying quality-of-service requirements while establishing priorities and promoting balance between the significantly heterogeneous services remains a key research problem.
In this paper, we use network slicing to study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems.
The limited fronthaul capacity and end-to-end delay constraints are simultaneously considered.
Optimizing baseband resources includes O-RAN radio unit (O-RU), physical resource block (PRB) assignment, and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.
Consequently, we break it down into two different steps and propose an iterative algorithm that finds a near-optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is resolved.
The proposed method is validated via simulations, which achieve a higher data rate and lower end-to-end delay than existing methods.
\end{abstract}
\begin{IEEEkeywords}
open radio access network (O-RAN), virtual network function (VNF), network slicing, knapsack problem, greedy algorithm, Karush-Kuhn-Tucker (KKT) Conditions.
\end{IEEEkeywords}
\section{Introduction}
%\subsection{State Of The Arts}
Network slicing is a key technology in 5G wireless systems. \textcolor{MidnightBlue}{Specifically, it isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various services} \cite{shen2020ai,setayesh2020joint,popovski20185g}.

There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). \textcolor{MidnightBlue}{Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.}
For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming. \textcolor{MidnightBlue}{Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries.} Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}

%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig. \ref{fig:c11}, is introduced to deal with these issues.

%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

%A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV). Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
%As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.

\subsection{Motivation}
\textcolor{MidnightBlue}{The optimal resource allocation for the 5G systems is crucial to reducing costs and improving user equipment (UE). Significant challenges face these systems, including interference alignment, limited capacity of the fronthaul links, energy restrictions on virtual machines (VMs), etc. }\cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.

\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations.}
%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig. \ref{fig:c11}, is introduced to deal with these issues.
\textcolor{MidnightBlue}{Unfortunately, the existing radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands. 
Hence, a new RAN paradigm, called open RAN (O-RAN) architecture, has emerged.
% as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost. Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges. 
Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.  
One of the fundamental problems lies in balancing services with different QoS, resource requirements, and priorities in O-RAN architecture}
 \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.  
%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}

The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
% Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.

\subsection{Main Contributions}
\textcolor{MidnightBlue}{This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.}
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item \textcolor{MidnightBlue}{We examine the problem of baseband resource allocation, such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN architecture. The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, are considered in this system. We take into account their corresponding QoS requirements and service priorities.}
\item We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
\item \textcolor{MidnightBlue}{We analyze the complexity of the proposed algorithms and demonstrate their convergence. Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.}
\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
\end{itemize}

\subsection{Organization}
%Table \ref{table:11a} lists the acronyms used throughout this paper, which
This paper is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel} and Section \ref{prS}, respectively. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper. For clarity, Table I lists the main acronyms used throughout the paper.

@@

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \vspace*{-2.5em}
 \end{table}

% \vspace*{-3em}
\section{Related Literature}\label{RL}
The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
\textcolor{MidnightBlue}{Two levels of dynamic network slicing in heterogeneous C-RAN (H-CRAN) are examined in \cite{lee2018dynamic}. The higher level manages user acceptance control, RRH association, and the allocation of BBU capacity. Meanwhile, PRB and power are allocated at lower levels.}
In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
\textcolor{MidnightBlue}{ In \cite{singh2022joint}, to provide 5G slicing services, the authors present a framework called O-RANFed that implements and optimizes federated learning tasks in O-RAN devices.}
\textcolor{MidnightBlue}{ Moreover, The authors of \cite{zhang2022federated} propose a federated deep reinforcement learning algorithm to achieve network slicing in O-RAN.}

\textcolor{MidnightBlue}{ Recent research has focused on multiplexing eMBB and URLLC services within a RAN.}
In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services. Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
In \cite{alsenwi2021intelligent}, the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

\textcolor{MidnightBlue}{In \cite{SystemCostMinimization,guo2016exploiting}, VMs activation and beamforming allocation are discussed in C-RAN systems.
Paper \cite{SystemCostMinimization} minimizes energy cost with system delay, fronthaul capacity, and rate constraints.
To guarantee UE delays, M/M/1 queueing theory is used for transmission and processing delays.}
In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated. Also, the association of RRH to the UE is considered and solved using innovative methods.

In \cite{ali2019energy,ali2018joint}, the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
Finally, in \cite{amani2019power}, the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved. 
%\vspace*{-1.8em}
\section{Background}\label{BG}
\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.36]{finalDraw1.pdf}
    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}
O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.

O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).  \textcolor{MidnightBlue}{By virtualizing RANs, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to their networks more quickly.} The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU). Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
 \textcolor{MidnightBlue}{Mostly non-real-time baseband processing occurs in the O-CU layer, while real-time baseband processing occurs in the O-DU layer.}

@@

@@

@@

This paper aims to maximize the sum-rate of all UEs subject to QoS constraints as follows. %{\color{red} where did you define the objective? what is R bar?}

@@

& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{c17}  \\

@@

 \label{prb0} \\

@@

>>>>

 %\pdfoutput=1
%\documentclass[conference]{IEEEtran}
\documentclass[lettersize,journal]{IEEEtran}
%\normalsize
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{setspace}
\usepackage{array,tabulary,tabularx,multirow}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{caption}
\captionsetup{font=footnotesize}
\usepackage{algcompatible}
%\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{stackengine}
%\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage[dvipsnames]{xcolor}
\usepackage{algorithm}
\usepackage{algorithmicx}
%\usepackage{algorithmic,algorithm2e,float}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{balance}
\usepackage{booktabs}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\setlength{\columnsep}{11mm}
\captionsetup{font=footnotesize}
\captionsetup[figure]{font=small}
\newcommand{\abstractnamefont}{\normalfont\small\bfseries}
\newcommand{\abstracttextfont}{\normalfont\small}
\setlength{\belowcaptionskip}{-10pt}
\def\hlinewd#1{%
\noalign{\ifnum0=`}\fi\hrule \@height #1 %
\futurelet\reserved@a\@xhline} 
%\setlength{\dbltextfloatsep}{-20pt}
\begin{document}

\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%}
\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, Saeede Parsaeefard$^\dagger$, and Onel Luis Alcaraz López$^\ddagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com, \{onel.alcarazlopez\}@oulu.fi\\
\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada, $^\ddagger$University of Oulu, Oulu, Finland}
 }
\maketitle
\pagenumbering{gobble}
%\vspace*{-4em}
\begin{abstract}
%\vspace*{-1.5em}
The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks. Nevertheless, strictly satisfying quality-of-service requirements while establishing priorities and promoting balance between the significantly heterogeneous services remains a key research problem.
In this paper, we use network slicing to study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems.
The limited fronthaul capacity and end-to-end delay constraints are simultaneously considered.
Optimizing baseband resources includes O-RAN radio unit (O-RU), physical resource block (PRB) assignment, and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.
Consequently, we break it down into two different steps and propose an iterative algorithm that finds a near-optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is resolved.
The proposed method is validated via simulations, which achieve a higher data rate and lower end-to-end delay than existing methods.
\end{abstract}
\begin{IEEEkeywords}
open radio access network (O-RAN), virtual network function (VNF), network slicing, knapsack problem, greedy algorithm, Karush-Kuhn-Tucker (KKT) Conditions.
\end{IEEEkeywords}
%
\vspace{-3mm}
\section{Introduction}
\vspace{-1mm}
%\subsection{State Of The Arts}
Network slicing is a key technology in 5G wireless systems. Specifically, it isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various services\cite{shen2020ai,setayesh2020joint,popovski20185g}.

There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.
For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming. Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries. Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig. \ref{fig:c11}, is introduced to deal with these issues.
%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence
%A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV). Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
%As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.
\vspace{-3mm}
\subsection{Motivation}
\vspace{-1mm}
The optimal resource allocation in 5G systems is crucial for reducing costs and improving the performance experienced by the user equipments (UEs).  These systems face significant challenges, including interference alignment, limited capacity of the fronthaul links, energy restrictions on virtual machines (VMs), etc.\cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.

Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations.
%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig. \ref{fig:c11}, is introduced to deal with these issues.
Unfortunately, the existing radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands. 
Hence, a new RAN paradigm, called open RAN (O-RAN) architecture, has emerged.
% as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost. Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges. 
Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.  
One of the fundamental problems lies in balancing services with different QoS, resource requirements, and priorities in O-RAN architecture
 \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.  
%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}

The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
% Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
\vspace{-3mm}
\subsection{Main Contributions}
\vspace{-1mm}
This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item We examine the problem of baseband resource allocation, such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs, to maximize the weighted throughput of the O-RAN architecture. The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, together with their corresponding QoS requirements and service priorities, are considered.
\item We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
\item We analyze the complexity of the proposed algorithms and demonstrate their convergence. Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.
\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
\end{itemize}
\vspace{-3mm}
\subsection{Organization}
\vspace{-1mm}
%Table \ref{table:11a} lists the acronyms used throughout this paper, which
This paper is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel} and Section \ref{prS}, respectively. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper. For clarity, Table I lists the main acronyms used throughout the paper.

@@

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \vspace*{-2.5em}
 \end{table}
\vspace{-3mm}
% \vspace*{-3em}
\section{Related Literature}\label{RL}
\vspace{-1mm}
The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
Two levels of dynamic network slicing in heterogeneous C-RAN (H-CRAN) are examined in \cite{lee2018dynamic}. The higher level manages user acceptance control, RRH association, and the allocation of BBU capacity. Meanwhile, PRB and power are allocated at lower levels.
In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
In \cite{singh2022joint}, to provide 5G slicing services, the authors present a framework called O-RANFed that implements and optimizes federated learning tasks in O-RAN devices.
Moreover, The authors of \cite{zhang2022federated} propose a federated deep reinforcement learning algorithm to achieve network slicing in O-RAN.

Recent research has focused on multiplexing eMBB and URLLC services within a RAN.
In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services. Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
In \cite{alsenwi2021intelligent}, the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

In \cite{SystemCostMinimization,guo2016exploiting}, VMs activation and beamforming allocation are discussed in C-RAN systems.
Paper \cite{SystemCostMinimization} minimizes energy cost with system delay, fronthaul capacity, and rate constraints.
To guarantee UE delays, M/M/1 queueing theory is used for transmission and processing delays.
In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated. Also, the association of RRH to the UE is considered and solved using innovative methods.

In \cite{ali2019energy,ali2018joint}, the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
Finally, in \cite{amani2019power}, the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved. 
%\vspace*{-1.8em}
%\vspace{-3mm}
\section{Background}\label{BG}
\vspace{-1mm}
\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.36]{fig/finalDraw1.pdf}
    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
    \vspace{-6mm}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
  \vspace{-2mm}
\end{figure}
O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.

O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN). By virtualizing RANs, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to their networks more quickly. The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU). Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
Mostly non-real-time baseband processing occurs in the O-CU layer, while real-time baseband processing occurs in the O-DU layer.

@@

\vspace{-3mm}

@@

\vspace{-1mm}

@@

This paper aims to maximize the sum-rate of all UEs subject to QoS constraints as follows %{\color{red} where did you define the objective? what is R bar?}

@@

& \sum\nolimits_{\forall r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{c17}  \\

@@

 \label{prb0}, \\

@@

\vspace{-2mm}
